Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-27 paper.tex
Minor edits

@@

\begin{abstract}
  \todo{The abstract goes here. DO NOT USE SPECIAL CHARACTERS,
    SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.}  Authors (final order
  to be discussed when the paper shapes up): Yongping/Val\'erie,
  Yuhong Yan, Tristan. Perhaps Pierre Bellec. \note{This is a note.}
\end{abstract}

@@

For simplicity, we assume that $m'$ represents an integer number $k$
of block rows (case 1, $k<\sqrt[3]{n}$), of complete rows (case 2,
$k<d$), of tile rows (case 3, $k<\sqrt[3]{n}$), of slices (case 4,
$k<d$) or of block slices (case 5, $k<\sqrt[3]{n}$) \todo{make a
  figure}. In each of these 5 cases, we define $v$ as follows:
\begin{equation*}
  v_1=db \text{ ; }  v_2=Db \text{ ; } v_3=Ddb \text{ ; } v_4=D^2b \text{ ; } v_5=D^2db
\end{equation*}
so that we have:
\begin{equation*}
k_i=\floor*{\frac{m}{v_i}} \quad \mathrm{and} \quad m_i'=k_iv_i, \quad i \in \llbracket 1,5 \rrbracket
\end{equation*}
Using these notations, the number of seeks performed by multiple reads is:
\begin{equation*}
  N_\mathrm{MR} =
\begin{cases}
  \floor*{\frac{Rb}{m_1'}}(k_1+1)+1
  + n \text{ mod } k_1& \text{if } d \leq \frac{m}{b} < D\\
  \ceil*{\frac{Rb}{m_2'}}(\sqrt[3]{n}+1)   & \text{if } D \leq \frac{m}{b} < Dd\\
  \floor*{\frac{Rb}{m_3'}}(k_3\sqrt[3]{n}+1)+1+\\
  \quad \quad \sqrt[3]{n}\left(\frac{n}{\sqrt[3]{n}} \text{ mod } k_3\right)&\
  \text{if } Dd \leq \frac{m}{b} < D^2\\
  \ceil*{\frac{Rb}{m_4'}}(\sqrt[3]{n}^2+1) & \text{if } D^2 \leq \frac{m}{b} < D^2d\\
  \floor*{\frac{Rb}{m_5'}}(k_5\sqrt[3]{n}^2+1)+1+&\\
  \quad \quad \sqrt[3]{n}^2\left(\frac{n}{\sqrt[3]{n}^2} \text{ mod } k_5\right)&\
  \text{if } D^2d \leq \frac{m}{b} < R
\end{cases}
\end{equation*}

@@

\subsection{Buffered slices vs slices}

\subsection{Cluster reads vs blocks and slices}

\subsection{Multiple reads vs blocks and slices}

>>>>

\author{Final ordering
  to be discussed when the paper: Yongping/Val\'erie,
  Yuhong Yan, Tristan.\\
  Department of Computer Science and Software Engineering, Concordia University, Montreal, Quebec, Canada
}

@@

\begin{abstract}
  \todo{The abstract goes here. DO NOT USE SPECIAL CHARACTERS,
    SYMBOLS, OR MATH IN YOUR TITLE OR ABSTRACT.} 
\end{abstract}

@@

For simplicity, we assume that $m'$ represents an integer number $k$
of block rows (case 1, $k<\sqrt[3]{n}$), of complete rows (case 2,
$k<d$), of tile rows (case 3, $k<\sqrt[3]{n}$), of slices (case 4,
$k<d$) or of block slices (case 5, $k<\sqrt[3]{n}$) \todo{make a
  figure}. In each of these 5 cases, we define $v$ as follows:
\begin{equation*}
  v_1=db \text{ ; }  v_2=Db \text{ ; } v_3=Ddb \text{ ; } v_4=D^2b \text{ ; } v_5=D^2db
\end{equation*}
so that we have:
\begin{equation*}
k_i=\floor*{\frac{m}{v_i}} \quad \mathrm{and} \quad m_i'=k_iv_i, \quad i \in \llbracket 1,5 \rrbracket
\end{equation*}
\todo{add one more preliminary step to explain how these equations were derived. Then jump to the final ones.}
Using these notations, the number of seeks performed by multiple reads is:
\begin{equation*}
  N_\mathrm{MR} =
\begin{cases}
  \floor*{\frac{Rb}{m_1'}}(k_1+1)+1
  + n \text{ mod } k_1& \text{if } d \leq \frac{m}{b} < D\\
  \ceil*{\frac{Rb}{m_2'}}(\sqrt[3]{n}+1)   & \text{if } D \leq \frac{m}{b} < Dd\\
  \floor*{\frac{Rb}{m_3'}}(k_3\sqrt[3]{n}+1)+1+\\
  \quad \quad \sqrt[3]{n}\left(\frac{n}{\sqrt[3]{n}} \text{ mod } k_3\right)&\
  \text{if } Dd \leq \frac{m}{b} < D^2\\
  \ceil*{\frac{Rb}{m_4'}}(\sqrt[3]{n}^2+1) & \text{if } D^2 \leq \frac{m}{b} < D^2d\\
  \floor*{\frac{Rb}{m_5'}}(k_5\sqrt[3]{n}^2+1)+1+&\\
  \quad \quad \sqrt[3]{n}^2\left(\frac{n}{\sqrt[3]{n}^2} \text{ mod } k_5\right)&\
  \text{if } D^2d \leq \frac{m}{b} < R
\end{cases}
\end{equation*}

@@

\subsection{Cluster reads}

\subsection{Multiple reads}
